---
title: Birthing the pregnancy package
author: Ella Kaye
date: 2025-09-17
date-format: long
format: 
  revealjs:
    theme: custom.scss
    highlight-style: ek-light.theme
    progress: false
    menu: false
execute:
  echo: true
  message: true
  warning: true
  error: true
---

```{r setup}
#| echo: false
options(crayon.enabled = TRUE)

ansi_aware_handler <- function(x, options) {
  paste0(
    "<pre class=\"r-output\"><code>",
    fansi::sgr_to_html(x = x, warn = FALSE, term.cap = "256"),
    "</code></pre>"
  )
}

knitr::knit_hooks$set(
  output = ansi_aware_handler, 
  message = ansi_aware_handler, 
  warning = ansi_aware_handler,
  error = ansi_aware_handler
)
```

## How it started...


```{.r}
how_far()
```


```
I am 15 weeks and 5 days pregnant.
All going well, I am due in 24 weeks and 2 days.
(That's 91 injections down, 170 to go...)
```


# {.center .center-h .larger150}

useful for [me]{.green-bg} → useful for [others]{.lime-bg}

. . .

[easy]{.blue-bg} and [personal]{.orange-bg}


# make the package a pleasure to use {.center .center-h .larger125 background-color="#D4006A"}

# {.center .center-h .larger150}

[tips]{.pink-bg} and [tricks]{.purple-bg}

. . .

`options` and `%||%`

. . . 

**{rlang}** and **{cli}**

. . .

utility and helper functions


## Pregnancy 1

```{r}
#| echo: false
#| output: false
library(pregnancy)
set_due_date("2025-12-01")
```

```{r}
library(pregnancy)
how_far()
```

## Pregnancy 2

```{r}
#| echo: false
#| output: false
set_due_date("2025-10-10")
set_person("I")
```

```{r}
how_far()
```

## Pregnancy 3

```{r}
#| echo: false
#| output: false
set_due_date("2026-01-20")
set_person("Ruth")
```

```{r}
how_far(on_date = "2025-12-25")
```

. . . 

```{r}
date_when(weeks = 33)
```

## NULL defaults

```{.r} 
how_far(
  on_date = Sys.Date(), 
  due_date = NULL, 
  person = NULL
)
```

## options and %||%

```{.r}
due_date <- due_date %||%
  getOption("pregnancy.due_date") %||%
  date_stop(due_date)
```

## Helpful errors with {rlang} and {cli}

```{r}
#| echo: false
#| output: false
set_due_date(NULL)
```


```{r}
#| eval: false
how_far()
```

. . .

```
`due_date` must have class <Date> or <character>.
ℹ It was NULL instead.
```
. . . 

```
ℹ You can do one of the following:
• set the `due_date` argument
• set the 'pregnancy.due_date' option for this R session with
  `set_due_date(due_date)`
• (recommended) set `options(pregnancy.due_date)` in your `.Rprofile`.
```
. . . 

```
ℹ See the pregnancy::pregnancy vignette for further details.
```


## ellakaye.github.io/pregnancy {.center-h}

![](images/pregnancy-hex-qr.svg){fig-align="center" width=120%}


# make your package a pleasure to use {.center .center-h .larger125 background-color="#006AD4"}


